---
title: "Lab7_guncontrol"
author: "Becky Clow"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
This: I'm Allison and I am editing this file. -Nice one I'm calling you this from now on --Eamon 

I'm Eamon and I'm also editing this file

```{r}

library(tidyverse)
gc_df <- read_csv("gc_df.csv")


```

We are asking is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get?).

On the 1st day the creator did some data science! 

Becky (the creator): Data wrangaling and counts

```{r}

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% # Created a contingency table
  select(-gender) # removes gender columns

rownames(get_guns) <- c("Female","Male") # naming the rows
```

On the 2nd day the creator deemed that a chi-square test shall be performed

My name is Eamon the collaborator and I'm going to be doing chi-square test for independence (I was appointed by the great creator)

"We ask if there is a significant association between recommended gun control action and sex (should guns be easier, harder, or the same difficulty to get?)."

```{r}

# Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1) # The "1" gives the margin of proportions -In this case run the proportions by the row (female, male)

guns_prop

# Run a chi-square test for independence 

guns_x2 <- chisq.test(get_guns)
guns_x2

```

Thus by the end of the second day, the recomended government action on gun access differed significantly between male (n = ) and female (n = ) respondents ($\chi^2$(`r guns_x2$parameter`)) =.... Notably, a much higher proportion of female respondents (57.4%) recomend making it more difficult to get guns compared to (40.4%) males. 



On the third day